### 2019-11-07 paper.tex
Initial import
 * Add a gitignore to skip output files
 * Include the IEEEtran.cls for proper rendering of LaTeX file
 * Copy the ieee conference template into paper.tex and start filling
   out some of the very basic fields near the top

\documentclass[conference]{IEEEtran}
%\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Conference Paper Title*\\
}

\author{\IEEEauthorblockN{Tim Upthegrove}
\IEEEauthorblockA{\textit{NCT} \\
\textit{Raytheon BBN Technologies}\\
Cambridge, MA, USA \\
tim.upthegrove@raytheon.com}
}

\maketitle

\begin{abstract}
The current implementation of Internet routing is described, a critical
weakness in the design is identified, and mitigation techniques for that
weakness are introduced.
\end{abstract}

\begin{IEEEkeywords}
Internet routing, BGP, RPKI, BGPSec
\end{IEEEkeywords}

\section{Introduction}
This document is a model and instructions for \LaTeX.
Please observe the conference page limits.

\section{Ease of Use}

\subsection{Maintaining the Integrity of the Specifications}

The IEEEtran class file is used to format your paper and style the text. All margins, 
column widths, line spaces, and text fonts are prescribed; please do not 
alter them. You may note peculiarities. For example, the head margin
measures proportionately more than is customary. This measurement 
and others are deliberate, using specifications that anticipate your paper 
as one part of the entire proceedings, and not as an independent document. 
Please do not revise any of the current designations.

\section{Prepare Your Paper Before Styling}
Before you begin to format your paper, first write and save the content as a 
separate text file. Complete all content and organizational editing before 
formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
proofreading, spelling and grammar.

Keep your text and graphic files separate until after the text has been 
formatted and styled. Do not number text heads---{\LaTeX} will do that 
for you.

\subsection{Abbreviations and Acronyms}\label{AA}
Define abbreviations and acronyms the first time they are used in the text, 
even after they have been defined in the abstract. Abbreviations such as 
IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
abbreviations in the title or heads unless they are unavoidable.

\subsection{Units}
\begin{itemize}
\item Use either SI (MKS) or CGS as primary units. (SI units are encouraged.) English units may be used as secondary units (in parentheses). An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds. This often leads to confusion because equations do not balance dimensionally. If you must use mixed units, clearly state the units for each quantity that you use in an equation.
\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''. Spell out units when they appear in text: ``. . . a few henries'', not ``. . . a few H''.
\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
\end{itemize}

\subsection{Equations}
Number equations consecutively. To make your 
equations more compact, you may use the solidus (~/~), the exp function, or 
appropriate exponents. Italicize Roman symbols for quantities and variables, 
but not Greek symbols. Use a long dash rather than a hyphen for a minus 
sign. Punctuate equations with commas or periods when they are part of a 
sentence, as in:
\begin{equation}
a+b=\gamma\label{eq}
\end{equation}

Be sure that the 
symbols in your equation have been defined before or immediately following 
the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
the beginning of a sentence: ``Equation \eqref{eq} is . . .''

\subsection{\LaTeX-Specific Advice}

Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
of ``hard'' references (e.g., \verb|(1)|). That will make it possible
to combine sections, add equations, or change the order of figures or
citations without having to go through the file line by line.

Please don't use the \verb|{eqnarray}| equation environment. Use
\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
environment leaves unsightly spaces around relation symbols.

Please note that the \verb|{subequations}| environment in {\LaTeX}
will increment the main equation counter even when there are no
equation numbers displayed. If you forget that, you might write an
article in which the equation numbers skip from (17) to (20), causing
the copy editors to wonder if you've discovered a new method of
counting.

{\BibTeX} does not work by magic. It doesn't get the bibliographic
data from thin air but from .bib files. If you use {\BibTeX} to produce a
bibliography you must send the .bib files.

{\LaTeX} can't read your mind. If you assign the same label to a
subsubsection and a table, you might find that Table I has been cross
referenced as Table IV-B3.

{\LaTeX} does not have precognitive abilities. If you put a
\verb|\label| command before the command that updates the counter it's
supposed to be using, the label will pick up the last counter to be
cross referenced instead. In particular, a \verb|\label| command
should not go before the caption of a figure or a table.

Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
will not stop equation numbers inside \verb|{array}| (there won't be
any anyway) and it might stop a wanted equation number in the
surrounding equation.

\subsection{Some Common Mistakes}\label{SCM}
\begin{itemize}
\item The word ``data'' is plural, not singular.
\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation. When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks. A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this). (A parenthetical sentence is punctuated within the parentheses.)
\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
\item Do not confuse ``imply'' and ``infer''.
\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
\end{itemize}
An excellent style manual for science writers is \cite{b7}.

\subsection{Authors and Affiliations}
\textbf{The class file is designed for, but not limited to, six authors.} A 
minimum of one author is required for all conference articles. Author names 
should be listed starting from left to right and then moving down to the 
next line. This is the author sequence that will be used in future citations 
and by indexing services. Names should not be listed in columns nor group by 
affiliation. Please keep your affiliations as succinct as possible (for 
example, do not differentiate among departments of the same organization).

\subsection{Identify the Headings}
Headings, or heads, are organizational devices that guide the reader through 
your paper. There are two types: component heads and text heads.

Component heads identify the different components of your paper and are not 
topically subordinate to each other. Examples include Acknowledgments and 
References and, for these, the correct style to use is ``Heading 5''. Use 
``figure caption'' for your Figure captions, and ``table head'' for your 
table title. Run-in heads, such as ``Abstract'', will require you to apply a 
style (in this case, italic) in addition to the style provided by the drop 
down menu to differentiate the head from the text.

Text heads organize the topics on a relational, hierarchical basis. For 
example, the paper title is the primary text head because all subsequent 
material relates and elaborates on this one topic. If there are two or more 
sub-topics, the next level head (uppercase Roman numerals) should be used 
and, conversely, if there are not at least two sub-topics, then no subheads 
should be introduced.

\subsection{Figures and Tables}
\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
bottom of columns. Avoid placing them in the middle of columns. Large 
figures and tables may span across both columns. Figure captions should be 
below the figures; table heads should appear above the tables. Insert 
figures and tables after they are cited in the text. Use the abbreviation 
``Fig.~\ref{fig}'', even at the beginning of a sentence.

\begin{table}[htbp]
\caption{Table Type Styles}
\begin{center}
\begin{tabular}{|c|c|c|c|}
\hline
\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
\cline{2-4} 
\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
\hline
copy& More table copy$^{\mathrm{a}}$& &  \\
\hline
\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
\end{tabular}
\label{tab1}
\end{center}
\end{table}

\begin{figure}[htbp]
\centerline{\includegraphics{fig1.png}}
\caption{Example of a figure caption.}
\label{fig}
\end{figure}

Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
rather than symbols or abbreviations when writing Figure axis labels to 
avoid confusing the reader. As an example, write the quantity 
``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
units in the label, present them within parentheses. Do not label axes only 
with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
quantities and units. For example, write ``Temperature (K)'', not 
``Temperature/K''.

\section*{Acknowledgment}

The preferred spelling of the word ``acknowledgment'' in America is without 
an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
acknowledgments in the unnumbered footnote on the first page.

\section*{References}

Please number citations consecutively within brackets \cite{b1}. The 
sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''

Number footnotes separately in superscripts. Place the actual footnote at 
the bottom of the column in which it was cited. Do not put footnotes in the 
abstract or reference list. Use letters for table footnotes.

Unless there are six authors or more give all authors' names; do not use 
``et al.''. Papers that have not been published, even if they have been 
submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
Capitalize only the first word in a paper title, except for proper nouns and 
element symbols.

For papers published in translation journals, please give the English 
citation first, followed by the original foreign-language citation \cite{b6}.

\begin{thebibliography}{00}
\bibitem{b1} G. Eason, B. Noble, and I. N. Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil. Trans. Roy. Soc. London, vol. A247, pp. 529--551, April 1955.
\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
\bibitem{b6} Y. Yorozu, M. Hirano, K. Oka, and Y. Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl. J. Magn. Japan, vol. 2, pp. 740--741, August 1987 [Digests 9th Annual Conf. Magnetics Japan, p. 301, 1982].
\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
\end{thebibliography}
\vspace{12pt}
\color{red}
IEEE conference templates contain guidance text for composing and formatting conference papers. Please ensure that all template text is removed from your conference paper prior to submission to the conference. Failure to remove the template text from your paper may result in your paper not being published.

\end{document}

### 2019-11-07 paper.tex
Layout the paper structure
 * Remove a bunch of the template text
 * Create an outline of the content

@@
 
-\title{Conference Paper Title*\\
-}
+\title{}
 
@@
 \begin{IEEEkeywords}
-Internet routing, BGP, RPKI, BGPSec
+Internet routing, BGP, BGP hijacking, RPKI, BGPSec
 \end{IEEEkeywords}
@@
 \section{Introduction}
-This document is a model and instructions for \LaTeX.
-Please observe the conference page limits.
 
-\section{Ease of Use}
+\section{Internet Routing}
+Individuals and organizations rely on Internet Service Providers (ISPs) to
+direct their network traffic to the appropriate destinations.  This section
+introduces how ISPs get traffic to the correct location by using the Border 
+Gateway Protocol (BGP).
 
-\subsection{Maintaining the Integrity of the Specifications}
+\subsection{Autonomous System Numbers}
+Any organization that wants to own IP addresses must also be assigned an
+Autonomous System Number.
 
-The IEEEtran class file is used to format your paper and style the text. All margins, 
-column widths, line spaces, and text fonts are prescribed; please do not 
-alter them. You may note peculiarities. For example, the head margin
-measures proportionately more than is customary. This measurement 
-and others are deliberate, using specifications that anticipate your paper 
-as one part of the entire proceedings, and not as an independent document. 
-Please do not revise any of the current designations.
+\subsection{IP Prefixes}
+IP addresses are typically assigned in contiguous blocks.  This is done
+intentionally,
 
-\section{Prepare Your Paper Before Styling}
-Before you begin to format your paper, first write and save the content as a 
-separate text file. Complete all content and organizational editing before 
-formatting. Please note sections \ref{AA}--\ref{SCM} below for more information on 
-proofreading, spelling and grammar.
+\subsection{BGP Operation}
 
-Keep your text and graphic files separate until after the text has been 
-formatted and styled. Do not number text heads---{\LaTeX} will do that 
-for you.
+\section{BGP Hijacking}
+ * Transitive trust
+ * Revisit example from introduction
 
-\subsection{Abbreviations and Acronyms}\label{AA}
-Define abbreviations and acronyms the first time they are used in the text, 
-even after they have been defined in the abstract. Abbreviations such as 
-IEEE, SI, MKS, CGS, ac, dc, and rms do not have to be defined. Do not use 
-abbreviations in the title or heads unless they are unavoidable.
+\section{BGP Hijacking Mitigation Techniques}
 
-\subsection{Units}
-\begin{itemize}
-\item Use either SI (MKS) or CGS as primary units.
-(SI units are encouraged.) English units may be used as secondary units (in parentheses).
-An exception would be the use of English units as identifiers in trade, such as ``3.5-inch disk drive''.
-\item Avoid combining SI and CGS units, such as current in amperes and magnetic field in oersteds.
-This often leads to confusion because equations do not balance dimensionally.
-If you must use mixed units, clearly state the units for each quantity that you use in an equation.
-\item Do not mix complete spellings and abbreviations of units: ``Wb/m\textsuperscript{2}'' or ``webers per square meter'', not ``webers/m\textsuperscript{2}''.
-Spell out units when they appear in text: ``.
-.
-.
-a few henries'', not ``.
-.
-.
-a few H''.
-\item Use a zero before decimal points: ``0.25'', not ``.25''. Use ``cm\textsuperscript{3}'', not ``cc''.)
-\end{itemize}
+\subsection{Filtering}
 
-\subsection{Equations}
-Number equations consecutively. To make your 
-equations more compact, you may use the solidus (~/~), the exp function, or 
-appropriate exponents. Italicize Roman symbols for quantities and variables, 
-but not Greek symbols. Use a long dash rather than a hyphen for a minus 
-sign. Punctuate equations with commas or periods when they are part of a 
-sentence, as in:
-\begin{equation}
-a+b=\gamma\label{eq}
-\end{equation}
+\subsection{Resource Public Key Infrastructure}
 
-Be sure that the 
-symbols in your equation have been defined before or immediately following 
-the equation. Use ``\eqref{eq}'', not ``Eq.~\eqref{eq}'' or ``equation \eqref{eq}'', except at 
-the beginning of a sentence: ``Equation \eqref{eq} is . . .''
-
-\subsection{\LaTeX-Specific Advice}
-
-Please use ``soft'' (e.g., \verb|\eqref{Eq}|) cross references instead
-of ``hard'' references (e.g., \verb|(1)|). That will make it possible
-to combine sections, add equations, or change the order of figures or
-citations without having to go through the file line by line.
-
-Please don't use the \verb|{eqnarray}| equation environment. Use
-\verb|{align}| or \verb|{IEEEeqnarray}| instead. The \verb|{eqnarray}|
-environment leaves unsightly spaces around relation symbols.
-
-Please note that the \verb|{subequations}| environment in {\LaTeX}
-will increment the main equation counter even when there are no
-equation numbers displayed. If you forget that, you might write an
-article in which the equation numbers skip from (17) to (20), causing
-the copy editors to wonder if you've discovered a new method of
-counting.
-
-{\BibTeX} does not work by magic. It doesn't get the bibliographic
-data from thin air but from .bib files. If you use {\BibTeX} to produce a
-bibliography you must send the .bib files.
-
-{\LaTeX} can't read your mind. If you assign the same label to a
-subsubsection and a table, you might find that Table I has been cross
-referenced as Table IV-B3.
-
-{\LaTeX} does not have precognitive abilities. If you put a
-\verb|\label| command before the command that updates the counter it's
-supposed to be using, the label will pick up the last counter to be
-cross referenced instead. In particular, a \verb|\label| command
-should not go before the caption of a figure or a table.
-
-Do not use \verb|\nonumber| inside the \verb|{array}| environment. It
-will not stop equation numbers inside \verb|{array}| (there won't be
-any anyway) and it might stop a wanted equation number in the
-surrounding equation.
-
-\subsection{Some Common Mistakes}\label{SCM}
-\begin{itemize}
-\item The word ``data'' is plural, not singular.
-\item The subscript for the permeability of vacuum $\mu_{0}$, and other common scientific constants, is zero with subscript formatting, not a lowercase letter ``o''.
-\item In American English, commas, semicolons, periods, question and exclamation marks are located within quotation marks only when a complete thought or name is cited, such as a title or full quotation.
-When quotation marks are used, instead of a bold or italic typeface, to highlight a word or phrase, punctuation should appear outside of the quotation marks.
-A parenthetical phrase or statement at the end of a sentence is punctuated outside of the closing parenthesis (like this).
-(A parenthetical sentence is punctuated within the parentheses.)
-\item A graph within a graph is an ``inset'', not an ``insert''. The word alternatively is preferred to the word ``alternately'' (unless you really mean something that alternates).
-\item Do not use the word ``essentially'' to mean ``approximately'' or ``effectively''.
-\item In your paper title, if the words ``that uses'' can accurately replace the word ``using'', capitalize the ``u''; if not, keep using lower-cased.
-\item Be aware of the different meanings of the homophones ``affect'' and ``effect'', ``complement'' and ``compliment'', ``discreet'' and ``discrete'', ``principal'' and ``principle''.
-\item Do not confuse ``imply'' and ``infer''.
-\item The prefix ``non'' is not a word; it should be joined to the word it modifies, usually without a hyphen.
-\item There is no period after the ``et'' in the Latin abbreviation ``et al.''.
-\item The abbreviation ``i.e.'' means ``that is'', and the abbreviation ``e.g.'' means ``for example''.
-\end{itemize}
-An excellent style manual for science writers is \cite{b7}.
-
-\subsection{Authors and Affiliations}
-\textbf{The class file is designed for, but not limited to, six authors.} A 
-minimum of one author is required for all conference articles. Author names 
-should be listed starting from left to right and then moving down to the 
-next line. This is the author sequence that will be used in future citations 
-and by indexing services. Names should not be listed in columns nor group by 
-affiliation. Please keep your affiliations as succinct as possible (for 
-example, do not differentiate among departments of the same organization).
-
-\subsection{Identify the Headings}
-Headings, or heads, are organizational devices that guide the reader through 
-your paper. There are two types: component heads and text heads.
-
-Component heads identify the different components of your paper and are not 
-topically subordinate to each other. Examples include Acknowledgments and 
-References and, for these, the correct style to use is ``Heading 5''. Use 
-``figure caption'' for your Figure captions, and ``table head'' for your 
-table title. Run-in heads, such as ``Abstract'', will require you to apply a 
-style (in this case, italic) in addition to the style provided by the drop 
-down menu to differentiate the head from the text.
-
-Text heads organize the topics on a relational, hierarchical basis. For 
-example, the paper title is the primary text head because all subsequent 
-material relates and elaborates on this one topic. If there are two or more 
-sub-topics, the next level head (uppercase Roman numerals) should be used 
-and, conversely, if there are not at least two sub-topics, then no subheads 
-should be introduced.
-
-\subsection{Figures and Tables}
-\paragraph{Positioning Figures and Tables} Place figures and tables at the top and 
-bottom of columns. Avoid placing them in the middle of columns. Large 
-figures and tables may span across both columns. Figure captions should be 
-below the figures; table heads should appear above the tables. Insert 
-figures and tables after they are cited in the text. Use the abbreviation 
-``Fig.~\ref{fig}'', even at the beginning of a sentence.
-
-\begin{table}[htbp]
-\caption{Table Type Styles}
-\begin{center}
-\begin{tabular}{|c|c|c|c|}
-\hline
-\textbf{Table}&\multicolumn{3}{|c|}{\textbf{Table Column Head}} \\
-\cline{2-4} 
-\textbf{Head} & \textbf{\textit{Table column subhead}}& \textbf{\textit{Subhead}}& \textbf{\textit{Subhead}} \\
-\hline
-copy& More table copy$^{\mathrm{a}}$& &  \\
-\hline
-\multicolumn{4}{l}{$^{\mathrm{a}}$Sample of a Table footnote.}
-\end{tabular}
-\label{tab1}
-\end{center}
-\end{table}
-
-\begin{figure}[htbp]
-\centerline{\includegraphics{fig1.png}}
-\caption{Example of a figure caption.}
-\label{fig}
-\end{figure}
-
-Figure Labels: Use 8 point Times New Roman for Figure labels. Use words 
-rather than symbols or abbreviations when writing Figure axis labels to 
-avoid confusing the reader. As an example, write the quantity 
-``Magnetization'', or ``Magnetization, M'', not just ``M''. If including 
-units in the label, present them within parentheses. Do not label axes only 
-with units. In the example, write ``Magnetization (A/m)'' or ``Magnetization 
-\{A[m(1)]\}'', not just ``A/m''. Do not label axes with a ratio of 
-quantities and units. For example, write ``Temperature (K)'', not 
-``Temperature/K''.
-
-\section*{Acknowledgment}
-
-The preferred spelling of the word ``acknowledgment'' in America is without 
-an ``e'' after the ``g''. Avoid the stilted expression ``one of us (R. B. 
-G.) thanks $\ldots$''. Instead, try ``R. B. G. thanks$\ldots$''. Put sponsor 
-acknowledgments in the unnumbered footnote on the first page.
-
-\section*{References}
-
-Please number citations consecutively within brackets \cite{b1}. The 
-sentence punctuation follows the bracket \cite{b2}. Refer simply to the reference 
-number, as in \cite{b3}---do not use ``Ref. \cite{b3}'' or ``reference \cite{b3}'' except at 
-the beginning of a sentence: ``Reference \cite{b3} was the first $\ldots$''
-
-Number footnotes separately in superscripts. Place the actual footnote at 
-the bottom of the column in which it was cited. Do not put footnotes in the 
-abstract or reference list. Use letters for table footnotes.
-
-Unless there are six authors or more give all authors' names; do not use 
-``et al.''. Papers that have not been published, even if they have been 
-submitted for publication, should be cited as ``unpublished'' \cite{b4}. Papers 
-that have been accepted for publication should be cited as ``in press'' \cite{b5}. 
-Capitalize only the first word in a paper title, except for proper nouns and 
-element symbols.
-
-For papers published in translation journals, please give the English 
-citation first, followed by the original foreign-language citation \cite{b6}.
-
-\begin{thebibliography}{00}
-\bibitem{b1} G.
-Eason, B.
-Noble, and I.
-N.
-Sneddon, ``On certain integrals of Lipschitz-Hankel type involving products of Bessel functions,'' Phil.
-Trans.
-Roy.
-Soc.
-London, vol.
-A247, pp.
-529--551, April 1955.
-\bibitem{b2} J. Clerk Maxwell, A Treatise on Electricity and Magnetism, 3rd ed., vol. 2. Oxford: Clarendon, 1892, pp.68--73.
-\bibitem{b3} I. S. Jacobs and C. P. Bean, ``Fine particles, thin films and exchange anisotropy,'' in Magnetism, vol. III, G. T. Rado and H. Suhl, Eds. New York: Academic, 1963, pp. 271--350.
-\bibitem{b4} K. Elissa, ``Title of paper if known,'' unpublished.
-\bibitem{b5} R. Nicole, ``Title of paper with only first word capitalized,'' J. Name Stand. Abbrev., in press.
-\bibitem{b6} Y.
-Yorozu, M.
-Hirano, K.
-Oka, and Y.
-Tagawa, ``Electron spectroscopy studies on magneto-optical media and plastic substrate interface,'' IEEE Transl.
-J.
-Magn.
-Japan, vol.
-2, pp.
-740--741, August 1987 [Digests 9th Annual Conf.
-Magnetics Japan, p.
-301, 1982].
-\bibitem{b7} M. Young, The Technical Writer's Handbook. Mill Valley, CA: University Science, 1989.
-\end{thebibliography}
-\vspace{12pt}
-\color{red}
-IEEE conference templates contain guidance text for composing and formatting conference papers.
-Please ensure that all template text is removed from your conference paper prior to submission to the conference.
-Failure to remove the template text from your paper may result in your paper not being published.
+\subsection{BGPsec}
 

### 2019-11-26 paper.tex
Update paper draft

@@
 \usepackage{algorithmic}
+\usepackage[bottom]{footmisc}
 \usepackage{graphicx}
@@
 
-\title{}
-
-\author{\IEEEauthorblockN{Tim Upthegrove}
-\IEEEauthorblockA{\textit{NCT} \\
-\textit{Raytheon BBN Technologies}\\
-Cambridge, MA, USA \\
-tim.upthegrove@raytheon.com}
-}
+\title{Chapter X Section Y: Internet Routing Security}
 
@@
 \begin{abstract}
-The current implementation of Internet routing is described, a critical
-weakness in the design is identified, and mitigation techniques for that
-weakness are introduced.
+This chapter introduces the weaknesses of Internet routing and how they can be addressed in practice.
 \end{abstract}
 
-\begin{IEEEkeywords}
-Internet routing, BGP, BGP hijacking, RPKI, BGPSec
-\end{IEEEkeywords}
+\section{Introduction}
+Imagine you are listening to a playlist on Youtube and the music suddenly stops.
+It seems like you still have access to other websites, so this must be a technical problem at Youtube, right?
+Back in 2008, something similar happened to people across the globe, but it had nothing to do with technical issues at Youtube.
+Instead, the state run network of Pakistan caused all Youtube traffic to be diverted into the network equivalent of a black hole.
+It turned out that Pakistan was simply trying to block Youtube for users within its borders, and yet it still managed to take Youtube down for almost all users across the world.
+How could a network in Pakistan cause users in Boston to be unable to reach services hosted in California?
+And if this is possible, couldn't this same technique be used by cyber criminals to steal sensitive information?
+In this section, we will address how this is possible and what can be done to mitigate it.
 
-\section{Introduction}
+\section{Internet Routing: Address and Number Assignment}
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/rirs.png}
+  \caption{Regional Internet Registries manage the IP block assignment and Autonomous Systsem Number assignment for geographically local areas.}
+  \label{fig:rirs}
+\end{figure}
 
-\section{Internet Routing}
-Individuals and organizations rely on Internet Service Providers (ISPs) to
-direct their network traffic to the appropriate destinations.  This section
-introduces how ISPs get traffic to the correct location by using the Border 
-Gateway Protocol (BGP).
+Before one can understand the weaknesses of Internet routing, one must understand how the Internet routing system is intended to work.
+Individuals and organizations rely on Internet Service Providers (ISPs) to direct their network traffic to the appropriate destinations.
+Any organization that wants to connect to the Internet must be given an IP address from an ISP or a block of IP addresses from a regional organization that manages IP address assignments known as a Regional Internet Registry (RIR).
+Figure \ref{fig:rirs} shows examples of RIRs and the regions which they manage the IP space for.
+Oragnizations that that want a set of their own IP addresses must also be assigned an Autonomous System Number (ASN).
+ASNs are unique numbers which identify an organization's network in the global Internet.
+It is common for a network to be assigned a single ASN and one or many contiguous blocks of IP addresses, as seen in Figure \ref{fig:rir-assignments}.
 
-\subsection{Autonomous System Numbers}
-Any organization that wants to own IP addresses must also be assigned an
-Autonomous System Number.
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/rir-assignments.jpg}
+  \caption{Regional Internet Registries often assign a single ASN for each organization.  They also often assign one or many contiguous IP blocks to those organizations.}
+  \label{fig:rir-assignments}
+\end{figure}
 
-\subsection{IP Prefixes}
-IP addresses are typically assigned in contiguous blocks.  This is done
-intentionally,
+\section{Internet Routing Operation}
+In order to reach a service like Youtube, users need to know how to reach the service.
+Youtube may have a set of IP addresses to allow users to connect to, but there are still two technical challenges:
+\begin{enumerate}
+ \item Youtube needs to announce where those IP addresses exist in the Internet
+ \item The Internet itself needs to announce the path to take in order to get there to potential users
+\end{enumerate}
+The Border Gateway Protocol (BGP) is used to solve these problems, and its operations are illustrated in Figure \ref{fig:bgp-ops}.
+The organization that owns the IP addresses announces those addresses as an IP prefix \footnote{An IP prefix could be one of the blocks assigned to the organization, or it could be a contiguous subset of IP addresses within that block.} into its upstream ISP, which takes care of challenge 1.
+In that same announcement, Youtube also announces its ASN.
+When Youtube's ISP connects to another network, it appends its own ASN to the list.
+This process continues throughout the Internet, allowing for each network to know which path or paths it can take to reach Youtube.
+These paths, known as AS paths, should all begin with Youtube's ASN, which effectively acts as a mapping between Youtube and the IP space in the global Internet.
+These AS paths are used to address challenge 2.
 
-\subsection{BGP Operation}
+If there are multiple paths to a target IP address, BGP uses a decision process similar to that in Figure \ref{fig:bgp-dec} \footnote{The BGP decision process is not standardized, and it may vary across different implementations.
+Many implementations are very similar.}.
+One of the most critical steps in the decision process, especially in the ISPs BGP decision making, is the AS path length.
+It is often the case that the path with the shortest AS path length is the preferred route for traffic to a destination with a given IP address.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/bgp-ops.jpg}
+  \caption{The Border Gateway Protocol is used to announce the source of IP prefixes into the global Internet and to create paths from other organization's networks to those IP addresses.}
+  \label{fig:bgp-ops}
+\end{figure}
+
+FIXME: need figure showing BGP decision process
 
 \section{BGP Hijacking}
- * Transitive trust
- * Revisit example from introduction
+With an understanding of how BGP operates, it is now useful to revisit the case of Youtube and the state run network of Pakistan.
+What happened was Pakistan's state run network attempted to take all traffic destined for IP addresses in Youtube's IP prefixes and send them to a place in its own internal network that connected to nothing.
+By mistake, this change in their internal network was announced, via BGP, to the rest of the world.
+Figure {fig:bgp-hijack} illustrates what may have happened for some users who experienced a Youtube outage.
+This problem is known as BGP Hijacking, and this example illustrates that the BGP has an inherent weakness: the receiver of the BGP announcement trusts the sender of the announcement, who in turn trusted the sender of the previous BGP announcement, and so on.
+This trust model is known as "transitive trust", and it is part of why BGP scales well and part of why BGP is not secure.
+BGP Hijacking can be unintentional, such as the Youtube example, but it can also be weaponized by others with malicious intent for data interception or denial of service.
+This is why it is so important that mitigation techniques be deployed across the Internet to avoid this weakness.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/bgp-hijack.jpg}
+  \caption{The state run network of Pakistan announced ownership of Youtube's IP prefixes to the rest of the world.  For many users, this ended up being the shortest AS path between them and Youtube.}
+  \label{fig:bgp-hijack}
+\end{figure}
 
 \section{BGP Hijacking Mitigation Techniques}
+There are various techniques which can me used to mitigate the weaknesses in BGP.
 

### 2019-12-01 paper.tex
Paper content largely done
 * All sections now have text
 * Word count currently way over
 * This is an interim checkin before culling text

@@
 
-\title{Chapter X Section Y: Internet Routing Security}
+\title{Internet Routing Security}
 
 \maketitle
-
-\begin{abstract}
-This chapter introduces the weaknesses of Internet routing and how they can be addressed in practice.
-\end{abstract}
 
@@
   \includegraphics[width=\linewidth]{images/bgp-ops.jpg}
-  \caption{The Border Gateway Protocol is used to announce the source of IP prefixes into the global Internet and to create paths from other organization's networks to those IP addresses.}
+  \caption{The Border Gateway Protocol is used to announce the source of IP prefixes into the global Internet and to create paths from other organization's networks to those IP addresses.
+The blue path represents the flow of BGP announcements for the Youtube IP prefix, and the green path represents the user's actual Youtube traffic.}
   \label{fig:bgp-ops}
 \end{figure}
-
-FIXME: need figure showing BGP decision process
 
@@
 BGP Hijacking can be unintentional, such as the Youtube example, but it can also be weaponized by others with malicious intent for data interception or denial of service.
+It turns out that both intentional and unintentional BGP hijacking occur on a near-daily basis[1].
 This is why it is so important that mitigation techniques be deployed across the Internet to avoid this weakness.
@@
   \includegraphics[width=\linewidth]{images/bgp-hijack.jpg}
-  \caption{The state run network of Pakistan announced ownership of Youtube's IP prefixes to the rest of the world.  For many users, this ended up being the shortest AS path between them and Youtube.}
+  \caption{The state run network of Pakistan announced ownership of Youtube's IP prefixes to the rest of the world.
+For many users, this ended up being the shortest AS path between them and Youtube.
+The blue path represents the flow of BGP announcements for the Youtube IP prefix, and the green path represents the user's actual Youtube traffic.}
   \label{fig:bgp-hijack}
@@
 \section{BGP Hijacking Mitigation Techniques}
-There are various techniques which can me used to mitigate the weaknesses in BGP.
+There are various techniques which can me used to mitigate the weaknesses in BGP, each with varying effectiveness and cost.
+Three techniques discussed below are Filtering, Resource Public Key Infrastructure (RPKI), and the BGPsec protocol.
 
 \subsection{Filtering}
+Filtering is a longstanding technique to both avoid accidental announcements as well as to prevent propagating incorrect announcements from neighbors.
+There are a litany of BGP filtering methods, but two examples are AS path filtering and IP prefix filtering.
+AS path filtering is a technique where only a set of whitelisted ASNs are allowed to be sent or accepted in BGP announcements.
+This can particularly be effective at ISPs which directly interface with organizations, as those ISPs can choose to only accept AS paths comprised of the organization's ASN.
+Organizations can similarly apply AS path filtering on egress of their announcements to avoid accidental propagation of incorrect ASNs.
+IP prefix filtering is similar to AS path filtering, only it is applied to specific whitelisted IP prefixes.
 
-\subsection{Resource Public Key Infrastructure}
+The primary upsides of filtering approaches are that they are widely available and they are computationally inexpensive.
+The downsides of filtering are that it is not a precise tool, and it can only be applied in certain cases.
+Furthermore, it needs to be configured case-by-case\footnote{For example, an ISP serving thousands of organizations would need to configure filtering for ASNs and IP prefixes for each organization individually.
+These values can change over time.}, making it rigid and difficult to maintain over time.
+Finally, filtering methods cannot be applied in all cases.
+They really need to be applied as close to the edge as possible, meaning the problems associated with transitive trust are still present.
+Filtering methods have been around for a long time, and given that BGP hijacking events are still relatively frequent, it is clear that newer methods should be deployed to secure Internet routing.
+
+\subsection{Resource Public Key Infrastructure for Origin Validation}
+At this point, an astute reader may have observed that the RIRs have a central mapping of IP prefixes to ASNs, and the first ASN in an ASN path should correspond to the associated IP prefix in an announcement.
+The question becomes, can this mapping of ASNs to IP prefixes be used to validate BGP announcements?
+This approach is commonly used by operators who are manually trying to uncover BGP Hijacking events after they have occurred, but it is also the primary concept behind Resource Public Key Infrastructure (RPKI).
+RPKI attempts to automate this approach by having a central authority (the RIRs in this case) host digitally signed information, known as Route Organization Authorizations (ROAs) confirming that an AS has the authority to announce a prefix.
+Different RIRs implement this in different ways, but one example is presented in Figure \ref{fig:rpki-assignment}.
+As shown in Figure \ref{fig:rpki-ops}, a BGP router can validate the origin of an announced prefix against the ROA database before it accepts the routes in the announcement.
+
+The upsides of RPKI are that it provides explicit protection against the issue seen in the Youtube incident, and it can be added onto existing Internet routing infrastructure with minor changes.
+The downside to RPKI is that it can be more computationally expensive\footnote{The cryptographic operations can be offloaded to a device which is attached to the router, which makes computational cost less of an issue} than standard BGP and it requires additional backend infrastructure which can result in more outages or misconfigurations, such as when a router is unable to obtain the latest ROAs to validate a new BGP announcement.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/rir-rpki-assignments.jpg}
+  \caption{This is an example of how ARIN implements RPKI.
+The organization is assigned an ASN and a set of IP blocks.
+If the organization participates in RPKI, then it generates a private key and a public certificate.
+It sends the public certificate to be signed by the RIR.
+The organization also generates ROA requests for its ASN and IP blocks, and it signs the request with its private key.
+If ARIN deems the ROA request valid, then it generates an ROA and places it in the ROA database, where it can be used to validate the origin of BGP prefixes.}
+  \label{fig:rpki-assignment}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/rpki-ops.jpg}
+  \caption{If RPKI origin validation is in use, then routers can verify each BGP announcement by verifying that the first ASN in the AS path matches the origin of the IP prefix in the ROA database.
+If there is a match, then the announcement is accepted and the associated routes may be propagated through the Internet.
+If there is no match, then the route in the advertisement can be rejected.}
+  \label{fig:rpki-ops}
+\end{figure}
 
 \subsection{BGPsec}
+RPKI does a good job of preventing a lot of BGP Hijacking issues, but it turns out that it doesn't resolve all of them.
+Go back to the case of malicious actors who want to intercept data.
+RPKI will prevent them from claiming ownership of an IP prefix which they do not own, but it does not prevent them from announcing an AS path through their network to an IP prefix associated with its correct ASN as illustrated in Figure \ref{fig:bgp-intercept}.
+Once traffic arrives in their network, they could either terminate it or passively spy on it.
+A protocol known as BGPsec attempts to mitigate this issue by leaning on the RPKI infrastructure not only for prefix origin validation, but also for hop-by-hop AS path change validation.
+BGPsec replaces the AS path with what it calls a BGPsec path, and it places extra requirements on how the path can be modified.
+First, the AS performing modification can only provide its own ASN along with the ASN of the neighbor that the BGPsec announcment is being sent too.
+Second, the AS originating the announcement must provide a signature creating using the organization's private key issued as part of RPKI which can validate that it added its ASN to the BGPsec path and that the announcement was intended for the recipient of the ASN.
+BGPsec operations are showin in Figure \ref{fig:bgpsec-ops}.
+
+The updsides of BGPsec are that it prevents all of the presented cases of BGP hijacking and it explicitly breaks the transitive trust property in BGP without losing the ability to scale.
+The downsides are that it requires significantly more computation\footnote{The announcement construction and cryptographic operations in BGPsec need to be performed per neighbor per prefix, whereas with standard BGP an announcement can be created with no cryptographic functions and then sent with multiple prefixes to all neighbors} full replacement of the existing Internet routing protocol.
+Also, while BGPsec does have an approach to allow for incremental adoption through interoperation with standard BGP, an advertisement where the full path is not secured through BGPsec is still susceptible to attack.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/bgp-intercept.jpg}
+  \caption{A malicious actor could announce a bogus route for a prefix with an AS path that includes the correct originating ASN and the malicious organization's ASN in the middle.
+The malicious organization could choose to either terminate the connection by doing something like hosting a fake version of Youtube, or they could pass the traffic along to the real Youtube and capture the traffic passing through for offline analysis.
+If this information includes encrypted financial information such as bank account numbers, then offline analysis could return highly valuable information.}
+  \label{fig:bgp-intercept}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/bgpsec-ops.jpg}
+  \caption{If BGPsec is in use, then routers can verify each BGP announcement by verifying that each ASN in the BGPsec path has signatures which match the ROA database.
+If each ASN in the path has valid signaturse, then the announcement is accepted and the associated routes may be propagated through the Internet.
+If any single ASN in the path does not match, or if the origin ASN does not own the advertised prefix according to the ROA database, then the route in the advertisement can be rejected.}
+  \label{fig:bgpsec-ops}
+\end{figure}
+
+\section{Conclusion}
+This chapter illustrated the key weakness of transitive trust in the Internet routing protocol known as BGP, and it showed how this weakness can be exploited through BGP hijacking.
+Multiple mitigation techniques for this weakness were introduced, including traditional approaches such filtering as well as newer approaches such as RPKI for origin validation and BGPsec.
+BGP hijacking has been shown to occur on a near-daily basis, and thus the traditional filtering methods were shown to be insufficient to address the BGP hijacking problem at Internet scale.
+
+[1] https://www.noction.com/blog/bgp-hijacking
 

### 2019-12-01 paper.tex
Initial culled version
 * Also added in missing bgpsec-ops images
 * Still 352 words over

--- 2019-11-07 paper.tex
@@
 
-\title{}
-
-\author{\IEEEauthorblockN{Tim Upthegrove}
-\IEEEauthorblockA{\textit{NCT} \\
-\textit{Raytheon BBN Technologies}\\
-Cambridge, MA, USA \\
-tim.upthegrove@raytheon.com}
-}
+\title{Internet Routing Security}
 
@@
 
-\begin{abstract}
-The current implementation of Internet routing is described, a critical
-weakness in the design is identified, and mitigation techniques for that
-weakness are introduced.
-\end{abstract}
+\section{Introduction}
+Imagine you are listening to a playlist on Youtube and the music suddenly stops.
+Other websites still work, so this must be a problem at Youtube, right?
+Back in 2008, something similar happened to people across the globe, but it was not caused by technical issues at Youtube.
+Instead, the state run network of Pakistan caused Youtube traffic to be diverted into the network equivalent of a black hole.
+It turned out that Pakistan was trying to block Youtube for users within its borders, but it still managed to take Youtube down for many users across the world.
+How could a network in Pakistan cause users in Boston to be unable to reach services hosted in California?
+And can this same technique be used by cyber criminals to steal sensitive information?
+This chapter presents why this is possible and what can be done to mitigate it.
 
-\begin{IEEEkeywords}
-Internet routing, BGP, BGP hijacking, RPKI, BGPSec
-\end{IEEEkeywords}
+\section{Internet Routing: Address and Number Assignment}
+Before understanding the weaknesses of Internet routing, one must understand how the Internet routing system is intended to work.
+Organizations rely on Internet Service Providers (ISPs) to direct their network traffic to the appropriate destinations.
+Any organization that wants to connect to the Internet must be loaned an IP address from an ISP or assigned a block of IP addresses from a \emph{Regional Internet Registry (RIR)}.
+RIRs manage IP address alloation for regions around the world, and Figure \ref{fig:rirs} shows examples of RIRs and their associated regions.
+As depicted in Figure \ref{fig:rir-assignments}, organizations that are assigned IP addresses by an RIR must also be assigned an \emph{Autonomous System Number (ASN)}.
+ASNs are unique numbers which identify an organization's network in the global Internet.
 
-\section{Introduction}
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/rirs.png}
+  \caption{Regional Internet Registries manage the IP block assignment and Autonomous Systsem Number assignment for geographically local areas.}
+  \label{fig:rirs}
+\end{figure}
 
-\section{Internet Routing}
-Individuals and organizations rely on Internet Service Providers (ISPs) to
-direct their network traffic to the appropriate destinations.  This section
-introduces how ISPs get traffic to the correct location by using the Border 
-Gateway Protocol (BGP).
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/rir-assignments.jpg}
+  \caption{Regional Internet Registries often assign a single ASN for each organization.  They also often assign one or many contiguous IP blocks to those organizations.}
+  \label{fig:rir-assignments}
+\end{figure}
 
-\subsection{Autonomous System Numbers}
-Any organization that wants to own IP addresses must also be assigned an
-Autonomous System Number.
+\section{Internet Routing Operation}
+In order to reach services like Youtube, users must be provided with a path to reach the service.
+Youtube may have a set of IP addresses to allow users to connect to, but there are still two technical challenges:
+\begin{enumerate}
+ \item Youtube needs to announce where those IP addresses exist in the Internet
+ \item The global Internet must find the paths to reach Youtube
+\end{enumerate}
+The \emph{Border Gateway Protocol (BGP)} is used to solve these problems, and its operation is illustrated in Figure \ref{fig:bgp-ops}.
+Continuing with the Youtube example, Youtube announces those addresses as an IP prefix \footnote{An IP prefix could be one of the blocks assigned to the organization, or it could be a contiguous subset of IP addresses within that block.} into its ISP, which takes care of challenge 1.
+In that same announcement, Youtube also announces its ASN.
+When Youtube's ISP connects to another network, it appends its own ASN after Youtube's ASN to make an ordered list that describes a path.
+This process continues throughout the Internet, allowing for each network to know which path or paths it can take to reach Youtube.
+These paths, known as \emph{AS paths}, all begin with Youtube's ASN, which maps Youtube's ASN to it's IP space in the global Internet.
+These AS paths are used to address challenge 2.
 
-\subsection{IP Prefixes}
-IP addresses are typically assigned in contiguous blocks.  This is done
-intentionally,
+If there are multiple paths to a target IP address, BGP uses a multi-step decision process to determine which route is preferred\footnote{The BGP decision process is not standardized, and it may vary across different implementations.
+Many implementations are very similar.}.
+One of the most critical steps in the decision process for ISPs is the AS path length.
+The path with the shortest AS path length to a given destination is often the preferred route.
 
-\subsection{BGP Operation}
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/bgp-ops.jpg}
+  \caption{The Border Gateway Protocol is used to announce the source of IP prefixes into the global Internet and to create paths from other organization's networks to those IP addresses.
+The blue path represents the flow of BGP announcements for the Youtube IP prefix, and the green path represents the user's actual Youtube traffic.}
+  \label{fig:bgp-ops}
+\end{figure}
 
 \section{BGP Hijacking}
- * Transitive trust
- * Revisit example from introduction
+Understanding how BGP operates, it is now helpful to revisit the Youtube outage previously introduced.
+Pakistan's state run network had attempted to take all traffic in its network destined for Youtube's IP prefixes and drop it.
+By mistake, this change in their internal network was announced to the rest of the Internet via BGP.
+Figure {fig:bgp-hijack} illustrates what may have happened for some users who experienced a Youtube outage.
+This was an example of \emph{BGP Hijacking}, and it illustrates that the BGP has an inherent weakness: the receiver of the BGP announcement trusts the sender of the announcement, who in turn trusted the sender of the previous BGP announcement, and so on.
+This trust model is known as \emph{transitive trust}, and it is part of why BGP scales well and part of why BGP is not secure.
+BGP Hijacking can be unintentional, such as the Youtube example, but it can also be weaponized by malicious actors for data interception, eavesdropping, or denial of service.
+Both intentional and unintentional BGP hijacking occur on a near-daily basis[1], emphasizing why it is critical to deploy mitigation techniques across the Internet.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/bgp-hijack.jpg}
+  \caption{The state run network of Pakistan announced ownership of Youtube's IP prefixes to the rest of the world.
+For many users, this ended up being the shortest AS path between them and Youtube.
+The blue path represents the flow of BGP announcements for the Youtube IP prefix, and the green path represents the user's actual Youtube traffic.}
+  \label{fig:bgp-hijack}
+\end{figure}
 
 \section{BGP Hijacking Mitigation Techniques}
+There are various techniques which can me used to mitigate the weaknesses in BGP, each with varying effectiveness and cost.
+Three techniques discussed below are \emph{Filtering}, \emph{Resource Public Key Infrastructure (RPKI)}, and the \emph{BGPsec} protocol.
+Filtering has been used for a number of years, while RPKI and BGPsec are only recently seeing adoption.
+A brief comparison of these models is presented at the end of this chapter, but a full comparison is ouside the scope of this text.
 
 \subsection{Filtering}
+Filtering is a longstanding technique to avoid accidental announcements and prevent propagating incorrect announcements from neighbors.
+There are numerous BGP filtering methods, but two examples are AS path filtering and IP prefix filtering.
+AS path filtering is a technique where only a set of whitelisted ASNs are allowed to be sent or accepted in BGP announcements.
+This is effective at ISPs which directly interface with organizations, as those ISPs can choose to only accept AS paths comprised of the organization's ASN\footnote{Organizations can similarly apply AS path filtering on egress of their announcements to avoid accidental propagation of incorrect ASNs}.
+IP prefix filtering is similar to AS path filtering, only it is applied to specific whitelisted IP prefixes.
+Filtering methods have been around for a long time, and given that BGP hijacking events are still relatively frequent, it is clear that newer methods should be deployed to secure Internet routing.
 
-\subsection{Resource Public Key Infrastructure}
+\subsection{Resource Public Key Infrastructure for Origin Validation}
+As noted previously, RIRs have a central mapping of IP prefixes to ASNs, and the first ASN in an ASN path should correspond to the associated IP prefix in an announcement.
+Can this mapping of ASNs to IP prefixes be used to validate the origin of BGP announcements?
+This approach is used by operators who uncover BGP Hijacking events after they have occurred, and it is also the primary concept behind Resource Public Key Infrastructure (RPKI).
+RPKI attempts to automate this approach by having the RIRs host digitally signed information, known as \emph{Route Organization Authorizations (ROAs)} confirming that an AS has the authority to announce an IP prefix.
+Different RIRs implement RPKI processes differently, but one example is presented in Figure \ref{fig:rpki-assignment}.
+Figure \ref{fig:rpki-ops} illustrates how a BGP router can validate the origin of an announced prefix.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/rir-rpki-assignments.jpg}
+  \caption{This is an example of how ARIN implements RPKI.
+The organization is assigned an ASN and a set of IP blocks.
+If the organization participates in RPKI, then it generates a private key and a public certificate.
+It sends the public certificate to be signed by the RIR.
+The organization also generates ROA requests for its ASN and IP blocks, and it signs the request with its private key.
+If ARIN deems the ROA request valid, then it generates an ROA and places it in the ROA database, where it can be used to validate the origin of BGP prefixes.}
+  \label{fig:rpki-assignment}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/rpki-ops.jpg}
+  \caption{If RPKI origin validation is in use, then routers can verify each BGP announcement by verifying that the first ASN in the AS path matches the origin of the IP prefix in the ROA database.
+If there is a match, then the announcement is accepted and the associated routes may be propagated through the Internet.
+If there is no match, then the route in the advertisement can be rejected.}
+  \label{fig:rpki-ops}
+\end{figure}
 
 \subsection{BGPsec}
+RPKI does a good job of preventing many BGP Hijacking issues, but it doesn't resolve all of them.
+Consider malicious actors who want to intercept data.
+RPKI mitigates claiming ownership of an IP prefix which they do not own, but it does not prevent them from creating a bogus announcement with an AS path through their network to an IP prefix associated with the correct ASN, as seen in Figure \ref{fig:bgp-inercept}.
+Once traffic arrives in the malicious organization's network, they can terminate it or observe and forward it.
+A protocol known as BGPsec attempts to mitigate this issue by leveraging the RPKI infrastructure not only for prefix origin validation, but also for hop-by-hop AS path change validation.
+BGPsec replaces the AS path with what it calls a \emph{BGPsec path}, and places requirements on how the path can be modified.
+First, the AS performing modification can only provide its own ASN along with the ASN of the neighbor that the BGPsec announcment is being sent to.
+Second, the AS originating the announcement must provide a signature using the organization's RPKI private key.
+Recipients of a BGPsec announcement can validate the ASNs in the BGPsec path by checking the associated signatures against the ROA database.
+Figure \ref{fig:bgpsec-ops} illustrates BGPsec operations.
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/bgp-intercept.jpg}
+  \caption{A malicious actor could announce a bogus route for a prefix with an AS path that includes the correct originating ASN and the malicious organization's ASN in the middle.
+The malicious organization could choose to either terminate the connection by doing something like hosting a fake version of Youtube, or they could pass the traffic along to the real Youtube and capture the traffic passing through for offline analysis.
+If this information includes encrypted financial information such as bank account numbers, then offline analysis could return highly valuable information.}
+  \label{fig:bgp-intercept}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\linewidth]{images/bgpsec-ops.jpg}
+  \caption{If BGPsec is in use, then routers can verify each BGP announcement by verifying that each ASN in the BGPsec path has signatures which match the ROA database.
+If each ASN in the path has valid signaturse, then the announcement is accepted and the associated routes may be propagated through the Internet.
+If any single ASN in the path does not match, or if the origin ASN does not own the advertised prefix according to the ROA database, then the route in the advertisement can be rejected.}
+  \label{fig:bgpsec-ops}
+\end{figure}
+
+FIXME: table
+ * Filtering:
+  * Upsides:
+   * Widely available
+   * Computationally inexpensive
+   * No coordination needed to set up
+  * Downsides:
+   * Can only be applied in certain cases near edge
+   * Configuration is rigid
+   * Empirically shown to be insufficient (near daily hijacking incidents)
+ * RPKI:
+  * Upsides:
+   * Mitigates some instances; would have prevented Youtube/Pakistan incident
+   * Can be added on to existing Internet routing system
+  * Downsides:
+   * Moderately more computationally expensive
+   * Can delay valid routing changes compared to unsecured BGP
+   * Requires additional backend setup and configuration
+   * Does not prevent malicious actors case
+ * BGPsec:
+  * Upsides:
+   * Can mitigate presented weaknesses; prevents malicious actors case
+   * Explicitly breaks transitive trust model 
+  * Downsides:
+   * Requires replacing entire Internet routing system for fully secure operation
+   * Significantly more computationally expensive
+   * Can delay valid routing changes compared to unsecured BGP
+
+\section{Conclusion}
+This chapter illustrated the key weakness of transitive trust in the Internet routing protocol known as BGP, and it showed how this weakness can be exploited through BGP hijacking.
+Multiple mitigation techniques for this weakness were introduced, including traditional approaches such filtering as well as newer approaches such as RPKI for origin validation and BGPsec.
+BGP hijacking has been shown to occur on a near-daily basis, and thus the traditional filtering methods were shown to be insufficient to address the BGP hijacking problem at Internet scale.
+
+[1] https://www.noction.com/blog/bgp-hijacking
 

### 2019-12-02 paper.tex
Fix images and cull more words
Down to 1282 word count.  May not be able to do much more.

@@
 \section{Internet Routing: Address and Number Assignment}
+\begin{figure}[b]
+  \includegraphics[width=\linewidth]{images/rirs.png}
+  \caption{Regional Internet Registries manage the IP block assignment and Autonomous Systsem Number assignment for geographically local areas.}
+  \label{fig:rirs}
+\end{figure}
 Before understanding the weaknesses of Internet routing, one must understand how the Internet routing system is intended to work.
@@
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/rirs.png}
-  \caption{Regional Internet Registries manage the IP block assignment and Autonomous Systsem Number assignment for geographically local areas.}
-  \label{fig:rirs}
+\begin{figure}[ht]
+  \begin{center}
+    \includegraphics[width=0.6\linewidth]{images/rir-assignments.jpg}
+  \end{center}
+  \caption{Regional Internet Registries often assign a single ASN for each organization.  They also often assign one or many contiguous IP blocks to those organizations.}
+  \label{fig:rir-assignments}
 \end{figure}
 
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/rir-assignments.jpg}
-  \caption{Regional Internet Registries often assign a single ASN for each organization.  They also often assign one or many contiguous IP blocks to those organizations.}
-  \label{fig:rir-assignments}
+\begin{figure}[hb]
+  \includegraphics[width=\linewidth]{images/bgp-ops.jpg}
+  \caption{The Border Gateway Protocol is used to announce the source of IP prefixes into the global Internet and to create paths from other organization's networks to those IP addresses.
+The blue path represents the flow of BGP announcements for the Youtube IP prefix, and the green path represents the user's actual Youtube traffic.}
+  \label{fig:bgp-ops}
 \end{figure}
@@
 The \emph{Border Gateway Protocol (BGP)} is used to solve these problems, and its operation is illustrated in Figure \ref{fig:bgp-ops}.
-Continuing with the Youtube example, Youtube announces those addresses as an IP prefix \footnote{An IP prefix could be one of the blocks assigned to the organization, or it could be a contiguous subset of IP addresses within that block.} into its ISP, which takes care of challenge 1.
+Continuing with the Youtube example, Youtube announces those addresses as an IP prefix\footnote{An IP prefix could be one of the blocks assigned to the organization, or it could be a contiguous subset of IP addresses within that block.} into its ISP, which takes care of challenge 1.
+
 In that same announcement, Youtube also announces its ASN.
@@
 Many implementations are very similar.}.
-One of the most critical steps in the decision process for ISPs is the AS path length.
+One of the most critical factors in the decision process for ISPs is the AS path length.
 The path with the shortest AS path length to a given destination is often the preferred route.
-
-\begin{figure}
-  \includegraphics[width=\linewidth]{images/bgp-ops.jpg}
-  \caption{The Border Gateway Protocol is used to announce the source of IP prefixes into the global Internet and to create paths from other organization's networks to those IP addresses.
-The blue path represents the flow of BGP announcements for the Youtube IP prefix, and the green path represents the user's actual Youtube traffic.}
-  \label{fig:bgp-ops}
-\end{figure}
 
@@
 Figure {fig:bgp-hijack} illustrates what may have happened for some users who experienced a Youtube outage.
-This was an example of \emph{BGP Hijacking}, and it illustrates that the BGP has an inherent weakness: the receiver of the BGP announcement trusts the sender of the announcement, who in turn trusted the sender of the previous BGP announcement, and so on.
-This trust model is known as \emph{transitive trust}, and it is part of why BGP scales well and part of why BGP is not secure.
-BGP Hijacking can be unintentional, such as the Youtube example, but it can also be weaponized by malicious actors for data interception, eavesdropping, or denial of service.
-Both intentional and unintentional BGP hijacking occur on a near-daily basis[1], emphasizing why it is critical to deploy mitigation techniques across the Internet.
+This was an example of \emph{BGP hijacking}, and it illustrates that the BGP has an inherent weakness: the receiver of the BGP announcement trusts the sender of the announcement, who in turn trusted the sender of the previous BGP announcement, and so on.
+This trust model is known as \emph{transitive trust}, and it is part of why BGP is not secure.
+BGP hijacking can be unintentional, such as the Youtube example, but it can also be intentionally performed by malicious actors for data interception, eavesdropping, or denial of service.
+Both intentional and unintentional BGP hijacking occur on a near-daily basis\cite{b1}.
 
-\begin{figure}
+\begin{figure}[ht]
   \includegraphics[width=\linewidth]{images/bgp-hijack.jpg}
@@
 \section{BGP Hijacking Mitigation Techniques}
-There are various techniques which can me used to mitigate the weaknesses in BGP, each with varying effectiveness and cost.
-Three techniques discussed below are \emph{Filtering}, \emph{Resource Public Key Infrastructure (RPKI)}, and the \emph{BGPsec} protocol.
+Multiple techniques exist to mitigate the weaknesses in BGP, each with varying effectiveness and cost.
+Three techniques discussed below are \emph{Filtering}, \emph{Resource Public Key Infrastructure (RPKI)}, and \emph{BGPsec}.
 Filtering has been used for a number of years, while RPKI and BGPsec are only recently seeing adoption.
-A brief comparison of these models is presented at the end of this chapter, but a full comparison is ouside the scope of this text.
+A brief comparison of these models is presented in Table \ref{tab:bgp-hijacking-comparison} at the end of this chapter.
 
 \subsection{Filtering}
-Filtering is a longstanding technique to avoid accidental announcements and prevent propagating incorrect announcements from neighbors.
-There are numerous BGP filtering methods, but two examples are AS path filtering and IP prefix filtering.
-AS path filtering is a technique where only a set of whitelisted ASNs are allowed to be sent or accepted in BGP announcements.
-This is effective at ISPs which directly interface with organizations, as those ISPs can choose to only accept AS paths comprised of the organization's ASN\footnote{Organizations can similarly apply AS path filtering on egress of their announcements to avoid accidental propagation of incorrect ASNs}.
+Filtering is a technique to prevent propagating incorrect announcements from neighbors.
+There are numerous BGP filtering methods, with two examples being AS path filtering and IP prefix filtering.
+AS path filtering only allows a set of whitelisted ASNs to be sent or accepted in BGP announcements.
+This is effective for ISPs near the edge of the Internet, as those ISPs can choose to only accept AS paths comprised of the organization's ASN\footnote{Organizations can similarly apply AS path filtering on egress of their announcements to avoid accidental propagation of incorrect ASNs}.
 IP prefix filtering is similar to AS path filtering, only it is applied to specific whitelisted IP prefixes.
-Filtering methods have been around for a long time, and given that BGP hijacking events are still relatively frequent, it is clear that newer methods should be deployed to secure Internet routing.
+Given that BGP hijacking events are still relatively frequent, it appears that filtering alone is insufficient to prevent BGP hijacking.
 
@@
 As noted previously, RIRs have a central mapping of IP prefixes to ASNs, and the first ASN in an ASN path should correspond to the associated IP prefix in an announcement.
-Can this mapping of ASNs to IP prefixes be used to validate the origin of BGP announcements?
-This approach is used by operators who uncover BGP Hijacking events after they have occurred, and it is also the primary concept behind Resource Public Key Infrastructure (RPKI).
+Can the mapping of ASNs to IP prefixes be used to validate the origin of BGP announcements?
+This approach is used by operators who uncover BGP hijacking events after they have occurred, and it is also the concept behind Resource Public Key Infrastructure (RPKI).
 RPKI attempts to automate this approach by having the RIRs host digitally signed information, known as \emph{Route Organization Authorizations (ROAs)} confirming that an AS has the authority to announce an IP prefix.
@@
 
-\begin{figure}
+\begin{figure}[hp]
   \includegraphics[width=\linewidth]{images/rir-rpki-assignments.jpg}
@@
 
-\begin{figure}
+\begin{figure}[hp]
   \includegraphics[width=\linewidth]{images/rpki-ops.jpg}
@@
 
-\subsection{BGPsec}
-RPKI does a good job of preventing many BGP Hijacking issues, but it doesn't resolve all of them.
-Consider malicious actors who want to intercept data.
-RPKI mitigates claiming ownership of an IP prefix which they do not own, but it does not prevent them from creating a bogus announcement with an AS path through their network to an IP prefix associated with the correct ASN, as seen in Figure \ref{fig:bgp-inercept}.
-Once traffic arrives in the malicious organization's network, they can terminate it or observe and forward it.
-A protocol known as BGPsec attempts to mitigate this issue by leveraging the RPKI infrastructure not only for prefix origin validation, but also for hop-by-hop AS path change validation.
-BGPsec replaces the AS path with what it calls a \emph{BGPsec path}, and places requirements on how the path can be modified.
-First, the AS performing modification can only provide its own ASN along with the ASN of the neighbor that the BGPsec announcment is being sent to.
-Second, the AS originating the announcement must provide a signature using the organization's RPKI private key.
-Recipients of a BGPsec announcement can validate the ASNs in the BGPsec path by checking the associated signatures against the ROA database.
-Figure \ref{fig:bgpsec-ops} illustrates BGPsec operations.
-
-\begin{figure}
+\begin{figure}[hp]
   \includegraphics[width=\linewidth]{images/bgp-intercept.jpg}
@@
 
-\begin{figure}
+\begin{figure}[hp]
   \includegraphics[width=\linewidth]{images/bgpsec-ops.jpg}
@@
 
-FIXME: table
- * Filtering:
-  * Upsides:
-   * Widely available
-   * Computationally inexpensive
-   * No coordination needed to set up
-  * Downsides:
-   * Can only be applied in certain cases near edge
-   * Configuration is rigid
-   * Empirically shown to be insufficient (near daily hijacking incidents)
- * RPKI:
-  * Upsides:
-   * Mitigates some instances; would have prevented Youtube/Pakistan incident
-   * Can be added on to existing Internet routing system
-  * Downsides:
-   * Moderately more computationally expensive
-   * Can delay valid routing changes compared to unsecured BGP
-   * Requires additional backend setup and configuration
-   * Does not prevent malicious actors case
- * BGPsec:
-  * Upsides:
-   * Can mitigate presented weaknesses; prevents malicious actors case
-   * Explicitly breaks transitive trust model 
-  * Downsides:
-   * Requires replacing entire Internet routing system for fully secure operation
-   * Significantly more computationally expensive
-   * Can delay valid routing changes compared to unsecured BGP
+\subsection{BGPsec}
+RPKI prevents many BGP hijacking issues, but it doesn't resolve all of them.
+Consider malicious actors who want to intercept data destined for Youtube.
+RPKI can detect the malicious network announcing it owns the Youtube IP space, but it cannot detect the case in Figure \ref{fig:bgp-intercept} of the malicious network announcing a path that passes through the malicious network but that eventually reaches Youtube, even if that path is bogus.
+This is another case of BGP hijacking.
+
+A protocol known as BGPsec attempts to mitigate this case by leveraging the RPKI infrastructure for both prefix origin validation and hop-by-hop path validation.
+BGPsec replaces the AS path with a \emph{BGPsec path} and places requirements on how the path can be modified.
+First, the AS performing modification can only provide its own ASN along with the ASN of the neighbor that the BGPsec announcment is being sent to.
+Second, the AS originating the announcement must provide a signature using the organization's RPKI private key.
+Recipients of a BGPsec announcement can validate the ASNs in the BGPsec path by checking the associated signatures against the ROA database.
+Figure \ref{fig:bgpsec-ops} illustrates BGPsec operations.
 
@@
 
-[1] https://www.noction.com/blog/bgp-hijacking
+\begin{thebibliography}{00}
+\bibitem{b1} https://www.noction.com/blog/bgp-hijacking
+\end{thebibliography}
 
+\newpage
+
+\begin{table*}
+\caption{Comparison of BGP Hijacking Mitigation Methods}
+\label{tab:bgp-hijacking-comparison}
+\begin{tabular}{|l|l|l|}
+\hline
+\textbf{Approach} & \textbf{Benefits}                                                                                                                                                      & \textbf{Drawbacks}                                                                                                                                                                                                                                   \\ \hline
+Filtering         & \begin{tabular}[c]{@{}l@{}} \textbullet Widely available\\ \textbullet Computationally inexpensive\\ \textbullet No coordination needed to set up\end{tabular}                                        & \begin{tabular}[c]{@{}l@{}} \textbullet Can only be applied in certain cases near edge\\ \textbullet Configuration is rigid\\ \textbullet Empirically shown to be insufficient\\   (near-daily   hijacking incidents)\end{tabular}                                                        \\ \hline
+RPKI              & \begin{tabular}[c]{@{}l@{}} \textbullet Mitigates many cases; would have prevented\\   Youtube/Pakistan incident\\ \textbullet Can be added on to existing Internet routing system\end{tabular} & \begin{tabular}[c]{@{}l@{}} \textbullet Moderately more computationally expensive\\ \textbullet Can delay valid routing changes compared\\   to unsecured BGP\\ \textbullet Requires additional backend setup and configuration\\ \textbullet Does not prevent malicious actors case\end{tabular} \\ \hline
+BGPsec            & \begin{tabular}[c]{@{}l@{}} \textbullet Can mitigate all presented weaknesses;\\   prevents malicious actors case\\ \textbullet Explicitly breaks transitive trust model\end{tabular}           & \begin{tabular}[c]{@{}l@{}} \textbullet Requires replacing entire Internet routing system\\   for fully secure operation\\ \textbullet Significantly more computationally expensive\\ \textbullet Can delay valid routing changes compared\\   to unsecured BGP\end{tabular}                \\ \hline
+\end{tabular}
+\end{table*}
 \end{document}

### 2019-12-02 paper.tex
Trim a few more words; still over

@@
 \section{Internet Routing Operation}
-In order to reach services like Youtube, users must be provided with a path to reach the service.
-Youtube may have a set of IP addresses to allow users to connect to, but there are still two technical challenges:
+In order to reach services like Youtube, users must be provided with a network path to reach the service.
+Youtube may have a set of IP addresses for users to connect, but there are still two challenges:
 \begin{enumerate}
  \item Youtube needs to announce where those IP addresses exist in the Internet
- \item The global Internet must find the paths to reach Youtube
+ \item The Internet must find paths to reach Youtube
 \end{enumerate}
-The \emph{Border Gateway Protocol (BGP)} is used to solve these problems, and its operation is illustrated in Figure \ref{fig:bgp-ops}.
-Continuing with the Youtube example, Youtube announces those addresses as an IP prefix\footnote{An IP prefix could be one of the blocks assigned to the organization, or it could be a contiguous subset of IP addresses within that block.} into its ISP, which takes care of challenge 1.
+The \emph{Border Gateway Protocol (BGP)} is used to solve these problems, as illustrated in Figure \ref{fig:bgp-ops}.
+Continuing with the Youtube example, Youtube announces its addresses as an IP prefix\footnote{An IP prefix could be one of the blocks assigned to the organization, or it could be a contiguous subset of IP addresses within that block.} into its ISP, which resolves challenge 1.
 
@@
 When Youtube's ISP connects to another network, it appends its own ASN after Youtube's ASN to make an ordered list that describes a path.
-This process continues throughout the Internet, allowing for each network to know which path or paths it can take to reach Youtube.
-These paths, known as \emph{AS paths}, all begin with Youtube's ASN, which maps Youtube's ASN to it's IP space in the global Internet.
+This process continues throughout the Internet, allowing for each network to know which paths it can take to reach Youtube.
+These paths, known as \emph{AS paths}, all begin with Youtube's ASN, which maps Youtube's ASN to its IP space in the global Internet.
 These AS paths are used to address challenge 2.
@@
 Many implementations are very similar.}.
-One of the most critical factors in the decision process for ISPs is the AS path length.
-The path with the shortest AS path length to a given destination is often the preferred route.
+The route with the shortest AS path length for a given destination is often the preferred route.
 
 \section{BGP Hijacking}
-Understanding how BGP operates, it is now helpful to revisit the Youtube outage previously introduced.
-Pakistan's state run network had attempted to take all traffic in its network destined for Youtube's IP prefixes and drop it.
+With an understanding of how BGP operates, it is helpful to revisit the Youtube outage previously introduced.
+Pakistan's state-run network had attempted to take all traffic in its network destined for Youtube's IP prefixes and drop it.
 By mistake, this change in their internal network was announced to the rest of the Internet via BGP.
 Figure {fig:bgp-hijack} illustrates what may have happened for some users who experienced a Youtube outage.
-This was an example of \emph{BGP hijacking}, and it illustrates that the BGP has an inherent weakness: the receiver of the BGP announcement trusts the sender of the announcement, who in turn trusted the sender of the previous BGP announcement, and so on.
+This was an example of \emph{BGP hijacking}, and it highlights a weakness in BGP: the receiver of the BGP announcement trusts the sender of the announcement, who trusted the sender of the previous BGP announcement, and so on.
 This trust model is known as \emph{transitive trust}, and it is part of why BGP is not secure.
@@
 \section{BGP Hijacking Mitigation Techniques}
-Multiple techniques exist to mitigate the weaknesses in BGP, each with varying effectiveness and cost.
-Three techniques discussed below are \emph{Filtering}, \emph{Resource Public Key Infrastructure (RPKI)}, and \emph{BGPsec}.
+Multiple techniques exist to address BGP hijacking, each with varying effectiveness and cost.
+Three such techniques are \emph{Filtering}, \emph{Resource Public Key Infrastructure (RPKI)}, and \emph{BGPsec}.
 Filtering has been used for a number of years, while RPKI and BGPsec are only recently seeing adoption.
-A brief comparison of these models is presented in Table \ref{tab:bgp-hijacking-comparison} at the end of this chapter.
+A brief comparison of these techniques is presented in Table \ref{tab:bgp-hijacking-comparison} at the end of this chapter.
 
@@
 There are numerous BGP filtering methods, with two examples being AS path filtering and IP prefix filtering.
-AS path filtering only allows a set of whitelisted ASNs to be sent or accepted in BGP announcements.
+AS path filtering only allows a set of whitelisted ASNs to be accepted in BGP announcements.
 This is effective for ISPs near the edge of the Internet, as those ISPs can choose to only accept AS paths comprised of the organization's ASN\footnote{Organizations can similarly apply AS path filtering on egress of their announcements to avoid accidental propagation of incorrect ASNs}.
 IP prefix filtering is similar to AS path filtering, only it is applied to specific whitelisted IP prefixes.
-Given that BGP hijacking events are still relatively frequent, it appears that filtering alone is insufficient to prevent BGP hijacking.
+Given that BGP hijacking events are still relatively frequent, filtering alone appears insufficient to prevent BGP hijacking.
 
 \subsection{Resource Public Key Infrastructure for Origin Validation}
-As noted previously, RIRs have a central mapping of IP prefixes to ASNs, and the first ASN in an ASN path should correspond to the associated IP prefix in an announcement.
-Can the mapping of ASNs to IP prefixes be used to validate the origin of BGP announcements?
+As noted previously, RIRs have a central mapping of IP prefixes to ASNs, and the first ASN in an AS path should correspond to the associated IP prefix in an announcement.
+The mapping of ASNs to IP prefixes be used to validate the origin of BGP announcements.
 This approach is used by operators who uncover BGP hijacking events after they have occurred, and it is also the concept behind Resource Public Key Infrastructure (RPKI).
-RPKI attempts to automate this approach by having the RIRs host digitally signed information, known as \emph{Route Organization Authorizations (ROAs)} confirming that an AS has the authority to announce an IP prefix.
-Different RIRs implement RPKI processes differently, but one example is presented in Figure \ref{fig:rpki-assignment}.
-Figure \ref{fig:rpki-ops} illustrates how a BGP router can validate the origin of an announced prefix.
+RPKI automates origin validation by having the RIRs host digitally signed information, known as \emph{Route Organization Authorizations (ROAs)} confirming that an AS has authority to originate an IP prefix.
+RPKI implementations vary by RIR, but one example is presented in Figure \ref{fig:rpki-assignment}.
+Figure \ref{fig:rpki-ops} shows RPKI origin validation in action.
 
@@
 \subsection{BGPsec}
-RPKI prevents many BGP hijacking issues, but it doesn't resolve all of them.
+RPKI prevents many cases of BGP hijacking, but it doesn't resolve all of them.
 Consider malicious actors who want to intercept data destined for Youtube.
-RPKI can detect the malicious network announcing it owns the Youtube IP space, but it cannot detect the case in Figure \ref{fig:bgp-intercept} of the malicious network announcing a path that passes through the malicious network but that eventually reaches Youtube, even if that path is bogus.
-This is another case of BGP hijacking.
+RPKI can detect a malicious network announcing it owns the Youtube IP space, but it cannot detect the case in Figure \ref{fig:bgp-intercept} of a malicious network announcing a path that passes through but does not originate from the malicious network, even if that path is fake.
 
-A protocol known as BGPsec attempts to mitigate this case by leveraging the RPKI infrastructure for both prefix origin validation and hop-by-hop path validation.
+A protocol known as BGPsec attempts to prevent this case by leveraging the RPKI infrastructure for full path validation.
 BGPsec replaces the AS path with a \emph{BGPsec path} and places requirements on how the path can be modified.
-First, the AS performing modification can only provide its own ASN along with the ASN of the neighbor that the BGPsec announcment is being sent to.
-Second, the AS originating the announcement must provide a signature using the organization's RPKI private key.
-Recipients of a BGPsec announcement can validate the ASNs in the BGPsec path by checking the associated signatures against the ROA database.
-Figure \ref{fig:bgpsec-ops} illustrates BGPsec operations.
+The AS constructing the announcement can only provide its own ASN and the ASN of the BGPsec announcment recipient.
+The AS constructing the announcement must provide a signature using the organization's RPKI private key.
+As shown in Figure \ref{fig:bgpsec-ops}, recipients of a BGPsec announcement can validate the chain of ASNs in the BGPsec path by checking the associated signatures against the ROA database.
 
@@
 This chapter illustrated the key weakness of transitive trust in the Internet routing protocol known as BGP, and it showed how this weakness can be exploited through BGP hijacking.
-Multiple mitigation techniques for this weakness were introduced, including traditional approaches such filtering as well as newer approaches such as RPKI for origin validation and BGPsec.
-BGP hijacking has been shown to occur on a near-daily basis, and thus the traditional filtering methods were shown to be insufficient to address the BGP hijacking problem at Internet scale.
+Filtering, RPKI, and BGPsec were introduced as techniques for addressing BGP hijacking.
 
